A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-09-03 rr-flow.Rmd
remove psych-data as there is no citation availible

How to best share a reproducible workflow? We believe that, ideally, a service provider should be found that guarantuees permanent and reliable hosting of the reproducible workflow, such as the Open Science Framework [@fosterOpenScienceFramework2017] or PsychData (citation needed), that is independ of Github, Docker Hub & MRAN. Second, to ensure that other users are legally able to benefit from the shared materials, authors must choose an appropriate license format. Typically, there is currently no single license that works for code, data, and media (such as text or figures). We encourage authors to choose appropriate license forms that do not hinder others from freely downloading, using, and moifying the shared workflows and materials while, at the same time, ensuring recognition for the time and effort invested in creating the workflow in the first place. In our experience, the Creative Commons license (CC-BY) is often appropriate for sharing texts, rmarkdown files, generated figures, and other media whereas scripts and any other computer code is often best shared according to the MIT license. Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work. These licenses are also in line with the recommendations by the Reproducibile Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].

>>>>

How to best share a reproducible workflow? We believe that, ideally, a service provider should be found that guarantuees permanent and reliable hosting of the reproducible workflow, such as the Open Science Framework [@fosterOpenScienceFramework2017], that is independ of Github, Docker Hub & MRAN. Second, to ensure that other users are legally able to benefit from the shared materials, authors must choose an appropriate license format. Typically, there is currently no single license that works for code, data, and media (such as text or figures). We encourage authors to choose appropriate license forms that do not hinder others from freely downloading, using, and moifying the shared workflows and materials while, at the same time, ensuring recognition for the time and effort invested in creating the workflow in the first place. In our experience, the Creative Commons license (CC-BY) is often appropriate for sharing texts, rmarkdown files, generated figures, and other media whereas scripts and any other computer code is often best shared according to the MIT license. Both licenses assure maximal freedom for future users while requiring the attribution of the original authors in derivative work. These licenses are also in line with the recommendations by the Reproducibile Research Standard [@stoddenEnhancingReproducibilityComputational2016; @stoddenEnablingReproducibleResearch2009].
